\documentclass[12pt,a4paper]{article}
\usepackage[UTF8]{ctex}     %先引入ctex
\usepackage[utf8]{inputenc} %再引入inputenc
\usepackage{graphicx}
\usepackage{lazylatex}
\usepackage{amsmath}
\usepackage{bookmark}
\usepackage{enumerate}
\tcbuselibrary{documentation}
\graphicspath{{img/}}
% 边距
\geometry{left=2.0cm,right=2.0cm,top=2.0cm,bottom=3.0cm}
% 大题
\newenvironment{problems}{\begin{list}{}{\renewcommand{\makelabel}[1]{\textbf{##1}\hfil}}}{\end{list}}
% 小题
\newenvironment{steps}{\begin{list}{}{\renewcommand{\makelabel}[1]{##1.\hfil}}}{\end{list}}
% 答
\providecommand{\ans}{\textbf{答}:~}
% 解
\providecommand{\sol}{\textbf{解}.~}

\begin{document}
\title{\normalsize \underline{操作系统(D)}\\\LARGE第 5 次作业}
\author{李子龙 518070910095}
\date{\today}
\maketitle

\begin{problems}
    \item[5.4] Consider the following set of processes, with the length of the CPU burst
    time given in milliseconds:

    \begin{tabular}{ccc}
        \underline{Process} & \underline{Burst Time} & \underline{Priority} \\
        $P_1$ & 2 & 2 \\
        $P_2$ & 1 & 1 \\
        $P_3$ & 8 & 4 \\
        $P_4$ & 4 & 2 \\
        $P_5$ & 5 & 3
    \end{tabular}

    The processes are assumed to have arrived in the order $P_1$, $P_2$, $P_3$, $P_4$, $P_5$,
    all at time 0.

    \begin{steps}
        \item[a] Draw four Gantt charts that illustrate the execution of these processes
        using the following scheduling algorithms: FCFS, SJF, nonpreemptive
        priority (a larger priority number implies a higher
        priority), and RR (quantum = 2).
        \item[b] What is the turnaround time of each process for each of the
        scheduling algorithms in part a?
        \item[c] What is the waiting time of each process for each of these scheduling
        algorithms?
        \item[d] Which of the algorithms results in the minimum average waiting
        time (over all processes)?
    \end{steps}

    \item[5.5] The following processes are being scheduled using a preemptive, roundrobin
    scheduling algorithm.

    \begin{tabular}{cccc}
        \underline{Process} & \underline{Priority} & \underline{Burst} & \underline{Arrival} \\
        $P_1$ & 40& 20& 0\\
        $P_2$ & 30& 25& 25\\
        $P_3$ & 30& 25& 30
\\        $P_4$ & 35& 15& 60
\\        $P_5$ & 5 &10 &100
\\        $P_6$ & 10& 10& 105
    \end{tabular}

    Each process is assigned a numerical priority,with a higher number indicating
a higher relative priority. In addition to the processes listed below,
the system also has an \textbf{idle task} (which consumes no CPU resources and
is identified as Pidle). This task has priority 0 and is scheduled whenever
the system has no other available processes to run. The length of a time quantum is 10 units. If a process is preempted by a higher-priority
process, the preempted process is placed at the end of the queue.

\begin{steps}
    \item[a] Show the scheduling order of the processes using a Gantt chart.
    \item[b] What is the turnaround time for each process?
    \item[c]  What is the waiting time for each process?
    \item[d] What is the CPU utilization rate?
\end{steps}

\item[5.10] The traditional UNIX scheduler enforces an inverse relationship between
priority numbers and priorities: the higher the number, the lower the
priority. The scheduler recalculates process priorities once per second
using the following function:
\begin{quotation}
    Priority = (recent CPU usage / 2) + base
\end{quotation}
where base = 60 and \emph{recent CPU usage} refers to a value indicating how
often a process has used the CPU since priorities were last recalculated.
Assume that recent CPU usage for process $P_1$ is 40, for process $P_2$ is 18,
and for process $P_3$ is 10. What will be the new priorities for these three
processes when priorities are recalculated? Based on this information,
does the traditional UNIX scheduler raise or lower the relative priority
of a CPU-bound process?

\item[5.18] The following processes are being scheduled using a preemptive,
priority-based, round-robin scheduling algorithm.

\begin{tabular}{cccc}
    \underline{Process} & \underline{Priority} & \underline{Burst} &  \underline{Arrival}\\
$P_1$ & 8 & 15& 0\\
$P_2$ & 3 & 20& 0\\
$P_3$ & 4 & 20& 20\\
$P_4$ & 4 & 20& 25\\
$P_5$ & 5 & 5 &45\\
$P_6$ & 5 & 15& 55
\end{tabular}

Each process is assigned a numerical priority,with a higher number indicating
a higher relative priority. The scheduler will execute the highestpriority
process. For processes with the same priority, a round-robin
scheduler will be used with a time quantum of 10 units. If a process is
preempted by a higher-priority process, the preempted process is placed
at the end of the queue.

\begin{steps}
    \item[a] Show the scheduling order of the processes using a Gantt chart.
    \item[b]  What is the turnaround time for each process?
    \item[c]  What is the waiting time for each process?
\end{steps}

\item[5.20] Which of the following scheduling algorithms could result in starvation?
\begin{steps}
    \item[a] First-come, first-served
    \item[b]  Shortest job first
    \item[c]  Round robin
    \item[d]  Priority
\end{steps} 

\end{problems}

\end{document}
